### 2024-08-12 simulation.qmd
20240605 - getting started/load packages
20240608 - getting started
Built site for gh-pages
20240703 - conclusion section
20240811 - fantasy football projections

>>>>

## Getting Started {#sec-simulationGettingStarted}

### Load Packages {#sec-simulationLoadPackages}

```{r}
library("tidyverse")
```

### Load Data {#sec-simulationLoadData}

```{r}
load(file = "./data/players_projectedPoints_seasonal.RData")
```

## Overview {#sec-simulationOverview}

## Simulation of Projected Statistics and Points {#sec-simulationProjectedPoints}

```{r}
calculate_fantasyPoints <- function(df, scoring_rules){
  #fantasyPoints <-

  #return(fantasyPoints)
}

monte_carlo_simulation <- function(position_df, num_simulations = 10000){
  player_ids <- unique(position_df$id)

  results <- lapply(player_ids, function(player_id){
    player_data <- position_df %>% filter(id == player_id)

    # Run the simulation for this player
    simulations <- replicate(num_simulations, {
      sampled_data <- player_data %>%
        summarise(across(
          c(pass_yds, pass_tds, rush_yds, rush_tds, rec_yds, rec_tds), 
          ~ if (all(is.na(.))) NA else sample(.[!is.na(.)], 1, replace = TRUE)))

      sampled_data
    }, simplify = FALSE)

    simulation_df <- bind_rows(simulations)
    #simulation_df$fantasyPoints <- calculate_fantasyPoints(simulation_df)

    ci <- simulation_df %>%
      summarise(across(where(is.numeric), list(
        lower = \(x) quantile(x, 0.025, na.rm = TRUE),
        upper = \(x) quantile(x, 0.975, na.rm = TRUE))))

    ci <- ci %>% mutate(id = player_id)

    return(ci)
    })

    # Combine results for all players
    final_ci <- bind_rows(results)

    return(final_ci)
}

monte_carlo_simulation(players_projectedPoints_seasonal$QB, num_simulations = 10)

QB_ci <- monte_carlo_simulation(players_projectedPoints_seasonal$QB)
```

## Conclusion {#sec-simulationConclusion}

::: {.content-visible when-format="html"}

## Session Info {#sec-simulationSessionInfo}

```{r}
sessionInfo()
```

:::
